\Title

### 2019-12-19 manuscript/manuscript.tex
Advances on manuscript

Potential field data, like gravity and magnetics, are useful for geophysics exploration.
The potential field data can be obtained from ground, airborne or satellite
measurements.
On ground surveys the data is often gathered on scattered points or following irregular
paths.
On airborne surveys the data is gathered on flight paths, producing a large number of
data points concentrated along almost straight lines.
To improve visualization of the data for interpretation and to prepare the data for
processing through different methods (RTP, upward continuation, Euler deconvolution,
etc), the data needs to be interpolated on a regular grid of data points.

@@

The most widely used source distribution is a set of point sources.
The potential field of point sources is easy to compute.
How to locate these point masses?
Existing approaches:
(i) one point source beneath each observation point at a constant depth (cite),
(ii) one point source beneath each observation point at a depth proportional to the
distance to its nearest data points (cite),
(iii) a regular grid of point sources (missing citations).

@@

>>>>

Potential field data, like gravity and magnetics, are useful for geophysics exploration.
The potential field data can be obtained from ground, airborne or satellite
measurements.
On ground surveys the data is often gathered on scattered points or following irregular
paths, usually at the topographic surface.
The data points have different heights.
On airborne surveys the data is gathered on flight paths, producing a large number of
data points concentrated along almost straight lines.
The height of measurement could change because of the vertical movement of the airship.
To improve visualization of the data for interpretation and to prepare the data for
processing through different methods (RTP, upward continuation, Euler deconvolution,
etc), the data needs to be interpolated on a regular grid of data points.

@@

The most widely used source distribution is a set of point sources.
The potential field of point sources is easy to compute.
\citet{barnes2011} make use of prisms.
How to locate these point masses?
Existing approaches:
(i) one point source beneath each observation point at a constant depth (cite),
(ii) one point source beneath each observation point at a depth proportional to the
distance to its nearest data points (cite),
(iii) a regular grid of sources \citep{barnes2011}.

@@

The choice of a source distribution is not trivial and plays an important role on the
accuracy of the predictions.

The most widely used source distributions are: a regular grid of point sources and
one point source beneath each observation point.

The \emph{regular grid} creates an homogeneous distribution of point sources bellow the
surveyed region.
It could create too many sources on areas without data and very few ones on
areas with a high number of observation points, leading to an underfitting of the
observed data.
This could be solved by reducing the grid spacing and therefore increasing the number of
point sources, heavily increasing the computational load of the interpolation process.

The \emph{source beneath data} layout adds sources where they are more needed.
If the survey is composed by a large number of data points clustered on paths
(like an airborne survey), putting one source beneath each observation point will create
an anisotropic source distribution: there will be several sources distributed along
a privileged direction.
This could introduce aliases on the predictions and increase the computational load for
fitting the predictor.

We propose a new source distribution that could simultaneously solve the problems of the
preceding ones: the \emph{block-median sources}.
It consist in dividing the region in blocks of equal size, computing the median location
of the observation points that fall inside each block, and putting one point source
bellow this block-median coordinate.
It creates one point source beneath each populated block, solving the problem of the
\emph{grid sources} layout, but also reducing the number of point sources in comparison
with the \emph{source beneath data} layout.

The depth of the point sources can be chosen following different criteria.
The most simple option is to locate all point sources at the same depth, which we will
call \emph{constant depth} in the future.
It could introduce some artifacts, like
